### 2014-05-20 learn_intro.tex
Clean up figure reference and add reference to contest results

When contending only with other endpoints of the same kind, the
``TCP-naive'' protocol achieved \textbf{55\% less queueing delay} than
the TCP-aware protocol. In other words, ``TCP-awareness'' has a cost
measured in lost performance when TCP cross-traffic is absent
(Figure~\ref{fig:tcpaware}).

But when contending against TCP, the ``TCP-naive'' protocol was
squeezed out by the more-aggressive cross-traffic. By contrast, the
``TCP-aware'' protocol achieved \textbf{36\% more throughput} and
\textbf{37\% less queueing delay} than the ``TCP-naive'' protocol,
and reached an equitable division of the available capacity with TCP.

>>>>

When contending only with other endpoints of the same kind, the
``TCP-naive'' protocol achieved \textbf{55\% less queueing delay} than
the TCP-aware protocol. In other words, ``TCP-awareness'' has a cost
measured in lost performance when TCP cross-traffic is absent
(Figure~\ref{fig:tcpawarehomo}).

But when contending against TCP, the ``TCP-naive'' protocol was
squeezed out by the more-aggressive cross-traffic. By contrast, the
``TCP-aware'' protocol achieved \textbf{36\% more throughput} and
\textbf{37\% less queueing delay} than the ``TCP-naive'' protocol,
and reached an equitable division of the available capacity with TCP
(Figure~\ref{fig:tcpawarehetero}).

### 2014-05-20 prevpub.tex
Remove Mosh for now
Clean up figure reference and add reference to contest results

@@

Chapter~\ref{chap:mosh}~revises a previous publication~\cite{mosh}:
K.~Winstein and H.~Balakrishnan.
\newblock {Mosh: An Interactive Remote Shell for Mobile Clients}.
\newblock In {\em USENIX Annual Technical Conference}, Boston, Mass., June
  2012.
}

>>>>

Chapter~\ref{chap:sprout}~also includes material from: A.~Sivaraman,
K.~Winstein, P.~Varley, S.~Das, J.~Ma, A.~Goyal, J.~Batalha, and
H.~Balakrishnan.  \newblock {Protocol Design Contests}.  \newblock
{\em SIGCOMM Computer Communications Review}, July 2014 (forthcoming).

@@

%Chapter~\ref{chap:mosh}~revises a previous publication~\cite{mosh}:
%K.~Winstein and H.~Balakrishnan.
%\newblock {Mosh: An Interactive Remote Shell for Mobile Clients}.
%\newblock In {\em USENIX Annual Technical Conference}, Boston, Mass., June
%  2012.
}
